---
title: "S-PRESTO child anthropometry description (fetal growth)"
author: "Meizhen Yao"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    highlight: tango
    df_print: paged
    fig_caption: yes
    fig_height: 7
    fig_width: 10
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    self_contained: yes
    code_folding: hide
    toc_depth: 6
header-includes: \usepackage{multirow}
---

<style type="text/css">
body{
  /*font-family: Helvetica;*/
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
options(digits = 4)
knitr::opts_chunk$set(echo = TRUE,tidy=TRUE,cache=F,warning = FALSE)
# suppress warning messages for final rendering
old.warn <- getOption("warn")
options(qwraps2_markup = "markdown")

```


```{r,message=FALSE,warning=FALSE,include=FALSE}
library(clubSandwich)
library(WeightIt)
library(ResourceSelection)
library(parameters)
library(sjstats)
library(rms)
library(survminer)
library(survival)
library(broom)
library("data.table")   
library(gtsummary)
library(gt)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(readxl)
library(sandwich)
library(boot)
library(table1)
library(flextable)
library(plyr)
library(Rcpp)
library(modelr)
library(lme4)
library(nlme)
library(readr)
library(gWQS)
library(broom.mixed)
library(yaml)
library(rmarkdown)
library(officer)
library(scales)
library(ipw)
library(spatstat)
library(survey)
library(MatchIt)
library(devtools)
library(cobalt)
# install_version("optmatch", version = "0.9.17", repos = "http://cran.us.r-project.org")
# install_github("markmfredrickson/RItools")
library(RItools)
library(optmatch)
library(mice)
library(gtsummary)
library(tidyr)
library(tidyverse)
library(grid)
library(gtable)
library(ggh4x)
library(naniar)
library(UpSetR)

#-------------------------------------------------------import data set
whole_cohort<-  read_csv("C:/Users/yaom03/OneDrive - The Mount Sinai Hospital/Documents/Projects/S-PRESTO/input/for paper/whole_cohort_20230316.csv")
fetal_growth<-  read_excel("C:/Users/yaom03/OneDrive - The Mount Sinai Hospital/Documents/Projects/S-PRESTO/input/Singapore/20231113_fetal_growth/ultrasound_CRF_20220218.xlsx", sheet = "Data")

fetal_growth<- whole_cohort %>% 
               left_join(fetal_growth, by = "Subject_ID") %>% 
               filter(participation==1)





old_name<- c("pgv2scanq9",
              'pgv3scanq4mm',
              'pgv4scanq7mm',
              'pgv5scanq7mm',
              'pgv2scanq10',
              'pgv3scanq5mm',
              'pgv4scanq8mm',
              'pgv5scanq8mm',
              'pgv2scanq11',
              'pgv3scanq7mm',
              'pgv4scanq9mm',
              'pgv5scanq9mm',
              'pgv2scanq13',
              'pgv3scanq8mm',
              'pgv4scanq10mm',
              'pgv5scanq10mm')

new_name<- c("BPD_pgv2",
              'BPD_pgv3',
              'BPD_pgv4',
              'BPD_pgv5',
              'HC_pgv2',
              'HC_pgv3',
              'HC_pgv4',
              'HC_pgv5',
              'AC_pgv2',
              'AC_pgv3',
              'AC_pgv4',
              'AC_pgv5',
              'FL_pgv2',
              'FL_pgv3',
              'FL_pgv4',
              'FL_pgv5')



setnames(fetal_growth, old = old_name, new = new_name)




```



# Fetal measurements summary statistics (in mm)
```{r, warning=FALSE, message=FALSE}
weight_table<-  fetal_growth %>%
              select(BPD_pgv2,
                    HC_pgv2,
                    AC_pgv2,
                    FL_pgv2,
                    BPD_pgv3,
                    HC_pgv3,
                    AC_pgv3,
                    FL_pgv3,
                    BPD_pgv4,
                    HC_pgv4,
                    AC_pgv4,
                    FL_pgv4,
                    BPD_pgv5,
                    HC_pgv5,
                    AC_pgv5,
                    FL_pgv5,
                    )%>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

weight_table
```



# Biparietal diameter (BPD)
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_weight_long <-  fetal_growth %>% 
                            pivot_longer(
                                    cols = starts_with("BPD_"),
                                    names_to = "BPD_time",
                                    names_prefix = "BPD_",
                                    values_to = "BPD_value",
                                    values_drop_na = FALSE
                                    ) 


blood_child_weight_long$BPD_time <- factor(blood_child_weight_long$BPD_time,
                                        levels = c("pgv2","pgv3", "pgv4", "pgv5"))

## assign visit variable
blood_child_weight_long_visit <- blood_child_weight_long %>%
  group_by(Subject_ID) %>%
  arrange(BPD_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_weight_plot1 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(x=BPD_value, fill=BPD_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(BPD_time), scale="free",independent = "all") 
               

blood_weight_plot1


blood_weight_plot2 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(y=BPD_value, x=BPD_time,fill=BPD_time)) + 
                         geom_boxplot()
               

blood_weight_plot2
```

# Head circumference (HC)
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_weight_long <-  fetal_growth %>% 
                            pivot_longer(
                                    cols = starts_with("HC_"),
                                    names_to = "HC_time",
                                    names_prefix = "HC_",
                                    values_to = "HC_value",
                                    values_drop_na = FALSE
                                    ) 


blood_child_weight_long$HC_time <- factor(blood_child_weight_long$HC_time,
                                        levels = c("pgv2","pgv3", "pgv4", "pgv5"))

## assign visit variable
blood_child_weight_long_visit <- blood_child_weight_long %>%
  group_by(Subject_ID) %>%
  arrange(HC_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_weight_plot1 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(x=HC_value, fill=HC_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(HC_time), scale="free",independent = "all") 
               

blood_weight_plot1


blood_weight_plot2 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(y=HC_value, x=HC_time,fill=HC_time)) + 
                         geom_boxplot()
               

blood_weight_plot2
```

# Abdominal circumference (AC)
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_weight_long <-  fetal_growth %>% 
                            pivot_longer(
                                    cols = starts_with("AC_"),
                                    names_to = "AC_time",
                                    names_prefix = "AC_",
                                    values_to = "AC_value",
                                    values_drop_na = FALSE
                                    ) 


blood_child_weight_long$AC_time <- factor(blood_child_weight_long$AC_time,
                                        levels = c("pgv2","pgv3", "pgv4", "pgv5"))

## assign visit variable
blood_child_weight_long_visit <- blood_child_weight_long %>%
  group_by(Subject_ID) %>%
  arrange(AC_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_weight_plot1 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(x=AC_value, fill=AC_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(AC_time), scale="free",independent = "all") 
               

blood_weight_plot1


blood_weight_plot2 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(y=AC_value, x=AC_time,fill=AC_time)) + 
                         geom_boxplot()
               

blood_weight_plot2
```



# Femur Length (FL)
## boxplot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_weight_long <-  fetal_growth %>% 
                            pivot_longer(
                                    cols = starts_with("FL_"),
                                    names_to = "FL_time",
                                    names_prefix = "FL_",
                                    values_to = "FL_value",
                                    values_drop_na = FALSE
                                    ) 


blood_child_weight_long$FL_time <- factor(blood_child_weight_long$FL_time,
                                        levels = c("pgv2","pgv3", "pgv4", "pgv5"))

## assign visit variable
blood_child_weight_long_visit <- blood_child_weight_long %>%
  group_by(Subject_ID) %>%
  arrange(FL_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_weight_plot1 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(x=FL_value, fill=FL_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(FL_time), scale="free",independent = "all") 
               

blood_weight_plot1


blood_weight_plot2 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(y=FL_value, x=FL_time,fill=FL_time)) + 
                         geom_boxplot()
               

blood_weight_plot2
```


# Estimated fetal weight (in gm)

Formula: Log10 weight = 1.3596 - 0.00386(AC x FL) + 0.0064 HC + 0.00061(BPD x AC) + 0.0424 AC + 0.174 FL 
note: Fetal measurements in cm; fetal weight in gm.

```{r, warning=FALSE, message=FALSE}

fetal_growth<- fetal_growth %>% 
               mutate(BPD_pgv2 = BPD_pgv2/10,
                    BPD_pgv3 = BPD_pgv3/10,
                    BPD_pgv4 = BPD_pgv4/10,
                    BPD_pgv5 = BPD_pgv5/10,
                    HC_pgv2 = HC_pgv2/10,
                    HC_pgv3 = HC_pgv3/10,
                    HC_pgv4 = HC_pgv4/10,
                    HC_pgv5 = HC_pgv5/10,
                    AC_pgv2 = AC_pgv2/10,
                    AC_pgv3 = AC_pgv3/10,
                    AC_pgv4 = AC_pgv4/10,
                    AC_pgv5 = AC_pgv5/10,
                    FL_pgv2 = FL_pgv2/10,
                    FL_pgv3 = FL_pgv3/10,
                    FL_pgv4 = FL_pgv4/10,
                    FL_pgv5 = FL_pgv5/10,
                    EFW_pgv2 = 10^(1.3596 - 0.00386*(AC_pgv2 * FL_pgv2) + 0.0064*HC_pgv2 + 0.00061*(BPD_pgv2 * AC_pgv2) + 0.0424*AC_pgv2 + 0.174*FL_pgv2),
                      EFW_pgv3 = 10^(1.3596 - 0.00386*(AC_pgv3 * FL_pgv3) + 0.0064*HC_pgv3 + 0.00061*(BPD_pgv3 * AC_pgv3) + 0.0424*AC_pgv3 + 0.174*FL_pgv3),
                      EFW_pgv4 = 10^(1.3596 - 0.00386*(AC_pgv4 * FL_pgv4) + 0.0064*HC_pgv4 + 0.00061*(BPD_pgv4 * AC_pgv4) + 0.0424*AC_pgv4 + 0.174*FL_pgv4),
                      EFW_pgv5 = 10^(1.3596 - 0.00386*(AC_pgv5 * FL_pgv5) + 0.0064*HC_pgv5 + 0.00061*(BPD_pgv5 * AC_pgv5) + 0.0424*AC_pgv5 + 0.174*FL_pgv5))


```


## summary statistics
```{r, warning=FALSE, message=FALSE}
weight_table<-  fetal_growth %>%
              select(EFW_pgv2,
                    EFW_pgv3,
                    EFW_pgv4,
                    EFW_pgv5)%>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

weight_table
```



## plot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_weight_long <-  fetal_growth %>% 
                            pivot_longer(
                                    cols = starts_with("EFW_"),
                                    names_to = "EFW_time",
                                    names_prefix = "EFW_",
                                    values_to = "EFW_value",
                                    values_drop_na = FALSE
                                    ) 


blood_child_weight_long$EFW_time <- factor(blood_child_weight_long$EFW_time,
                                        levels = c("pgv2","pgv3", "pgv4", "pgv5"))

## assign visit variable
blood_child_weight_long_visit <- blood_child_weight_long %>%
  group_by(Subject_ID) %>%
  arrange(EFW_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_weight_plot1 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(x=EFW_value, fill=EFW_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(EFW_time), scale="free",independent = "all") 
               

blood_weight_plot1


blood_weight_plot2 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(y=EFW_value, x=EFW_time,fill=EFW_time)) + 
                         geom_boxplot()
               

blood_weight_plot2
```



# missing visualization
```{r, warning=FALSE, message=FALSE}

blood_child_weight<- fetal_growth %>% 
                     select(
                       Subject_ID,
                       BPD_pgv2,
                    BPD_pgv3,
                    BPD_pgv4,
                    BPD_pgv5,
                    HC_pgv2,
                    HC_pgv3,
                    HC_pgv4,
                    HC_pgv5,
                    AC_pgv2,
                    AC_pgv3,
                    AC_pgv4,
                    AC_pgv5,
                    FL_pgv2,
                    FL_pgv3,
                    FL_pgv4,
                    FL_pgv5,
                    EFW_pgv2,
                    EFW_pgv3,
                    EFW_pgv4,
                    EFW_pgv5)

vis_miss(blood_child_weight)
gg_miss_var(blood_child_weight)

blood_child_weight_complete<- blood_child_weight[complete.cases(blood_child_weight),]
nrow(blood_child_weight_complete)
# n=149


```

# missing visualization (at least with pgv3 measurement, and combine with child anthropometry)
```{r, warning=FALSE, message=FALSE}
blood_child_weight_del_m18<- blood_child_weight[complete.cases(blood_child_weight[,c('BPD_pgv3', "HC_pgv3", "AC_pgv3", "FL_pgv3", "EFW_pgv3")]),]
nrow(blood_child_weight_del_m18)
#n=297
blood_child_del_m18<- read_csv("C:/Users/yaom03/OneDrive - The Mount Sinai Hospital/Documents/Projects/S-PRESTO/input/anthropometry/blood_child_who_stan_impute_mix_dropwk1_11162023.csv")

common_id<- intersect(blood_child_del_m18$Subject_ID, blood_child_weight_del_m18$Subject_ID)
length(common_id)
# [1] 223

vis_miss(blood_child_weight_del_m18[blood_child_weight_del_m18$Subject_ID%in%common_id,])
gg_miss_var(blood_child_weight_del_m18)
```




