---
title: "S-PRESTO child anthropometry description (restricted & complete.cases)"
author: "Meizhen Yao"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    highlight: tango
    df_print: paged
    fig_caption: yes
    fig_height: 7
    fig_width: 10
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    self_contained: yes
    code_folding: hide
    toc_depth: 6
header-includes: \usepackage{multirow}
---

<style type="text/css">
body{
  /*font-family: Helvetica;*/
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
options(digits = 4)
knitr::opts_chunk$set(echo = TRUE,tidy=TRUE,cache=F,warning = FALSE)
# suppress warning messages for final rendering
old.warn <- getOption("warn")
options(qwraps2_markup = "markdown")

```


```{r,message=FALSE,warning=FALSE,include=FALSE}
library(clubSandwich)
library(WeightIt)
library(ResourceSelection)
library(parameters)
library(sjstats)
library(rms)
library(survminer)
library(survival)
library(broom)
library("data.table")   
library(gtsummary)
library(gt)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(readxl)
library(sandwich)
library(boot)
library(table1)
library(flextable)
library(plyr)
library(Rcpp)
library(modelr)
library(lme4)
library(nlme)
library(readr)
library(gWQS)
library(broom.mixed)
library(yaml)
library(rmarkdown)
library(officer)
library(scales)
library(ipw)
library(spatstat)
library(survey)
library(MatchIt)
library(devtools)
library(cobalt)
# install_version("optmatch", version = "0.9.17", repos = "http://cran.us.r-project.org")
# install_github("markmfredrickson/RItools")
library(RItools)
library(optmatch)
library(mice)
library(gtsummary)
library(tidyr)
library(tidyverse)
library(grid)
library(gtable)
library(ggh4x)
library(naniar)
library(UpSetR)

#-------------------------------------------------------import data set
blood_child_who_stan<- read_csv("C:/Users/yaom03/OneDrive - The Mount Sinai Hospital/Documents/Projects/S-PRESTO/input/anthropometry/blood_child_who_stan_complete_dropwk1_06062023.csv")


 

```


# Weight
## summary statistics
```{r, warning=FALSE, message=FALSE}
weight_table<-  blood_child_who_stan %>%
              select(weight_del_merge,
                     weight_wk1,
                     weight_wk3,
                     weight_wk6,
                     weight_m3,
                     weight_m6,
                     weight_m12,
                     weight_m18)%>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

weight_table
```


## missing visualization
```{r, warning=FALSE, message=FALSE}

blood_child_weight<- blood_child_who_stan %>% 
                     select(starts_with("weight_"))


vis_miss(blood_child_weight)
gg_miss_var(blood_child_weight)

```


## boxplot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_weight_long <- blood_child_who_stan %>% 
                          pivot_longer(
                                  cols = starts_with("weight_"),
                                  names_to = "weight_time",
                                  names_prefix = "weight_",
                                  values_to = "weight_value",
                                  values_drop_na = FALSE
                                  ) 


blood_child_weight_long$weight_time <- factor(blood_child_weight_long$weight_time,
                                        levels = c("del_merge","wk1", "wk3", "wk6", "m3", "m6", "m12", "m18"))

## assign visit variable
blood_child_weight_long_visit <- blood_child_weight_long %>%
  group_by(Subject_ID) %>%
  arrange(weight_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_weight_plot1 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(x=weight_value, fill=weight_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(weight_time), scale="free",independent = "all") 
               

blood_weight_plot1


blood_weight_plot2 <- blood_child_weight_long_visit %>% 
                         ggplot(aes(y=weight_value, x=weight_time,fill=weight_time)) + 
                         geom_boxplot()
               

blood_weight_plot2
```




# Length
## summary statistics
```{r, warning=FALSE, message=FALSE}
length_table<-  blood_child_who_stan %>%
              select(length_del_merge,
                     length_wk1,
                     length_wk3,
                     length_wk6,
                     length_m3,
                     length_m6,
                     length_m12,
                     length_m18)%>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

length_table
```



## missing visualization
```{r, warning=FALSE, message=FALSE}

blood_child_length<- blood_child_who_stan %>% 
                     select(starts_with("length_"))


vis_miss(blood_child_length)
gg_miss_var(blood_child_length)

```

## boxplot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_length_long <- blood_child_who_stan %>% 
                          pivot_longer(
                                  cols = starts_with("length_"),
                                  names_to = "length_time",
                                  names_prefix = "length_",
                                  values_to = "length_value",
                                  values_drop_na = FALSE
                                  ) 


blood_child_length_long$length_time <- factor(blood_child_length_long$length_time,
                                        levels = c("del_merge","wk1", "wk3", "wk6", "m3", "m6", "m12", "m18"))

## assign visit variable
blood_child_length_long_visit <- blood_child_length_long %>%
  group_by(Subject_ID) %>%
  arrange(length_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_child_length_plot1 <- blood_child_length_long_visit %>% 
                         ggplot(aes(x=length_value, fill=length_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(length_time), scale="free",independent = "all") 
               

blood_child_length_plot1


blood_child_length_plot2 <- blood_child_length_long_visit %>% 
                         ggplot(aes(y=length_value, x=length_time,fill=length_time)) + 
                         geom_boxplot()
               

blood_child_length_plot2
```





# zweight
## summary statistics
```{r, warning=FALSE, message=FALSE}
zweight_table<-  blood_child_who_stan %>%
              select(zweight_del_merge,
                     zweight_wk1,
                     zweight_wk3,
                     zweight_wk6,
                     zweight_m3,
                     zweight_m6,
                     zweight_m12,
                     zweight_m18)%>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

zweight_table
```



## missing visualization
```{r, warning=FALSE, message=FALSE}

blood_child_zweight<- blood_child_who_stan %>% 
                     select(starts_with("zweight_"))


vis_miss(blood_child_zweight)
gg_miss_var(blood_child_zweight)

```

## boxplot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_zweight_long <- blood_child_who_stan %>% 
                          pivot_longer(
                                  cols = starts_with("zweight_"),
                                  names_to = "zweight_time",
                                  names_prefix = "zweight_",
                                  values_to = "zweight_value",
                                  values_drop_na = FALSE
                                  ) 


blood_child_zweight_long$zweight_time <- factor(blood_child_zweight_long$zweight_time,
                                        levels = c("del_merge","wk1", "wk3", "wk6", "m3", "m6", "m12", "m18"))

## assign visit variable
blood_child_zweight_long_visit <- blood_child_zweight_long %>%
  group_by(Subject_ID) %>%
  arrange(zweight_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_child_zweight_plot1 <- blood_child_zweight_long_visit %>% 
                         ggplot(aes(x=zweight_value, fill=zweight_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(zweight_time), scale="free",independent = "all") 
               

blood_child_zweight_plot1


blood_child_zweight_plot2 <- blood_child_zweight_long_visit %>% 
                         ggplot(aes(y=zweight_value, x=zweight_time,fill=zweight_time)) + 
                         geom_boxplot()
               

blood_child_zweight_plot2
```

# zlength
## summary statistics
```{r, warning=FALSE, message=FALSE}
zlength_table<-  blood_child_who_stan %>%
              select(zlength_del_merge,
                     zlength_wk1,
                     zlength_wk3,
                     zlength_wk6,
                     zlength_m3,
                     zlength_m6,
                     zlength_m12,
                     zlength_m18) %>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

zlength_table
```



## missing visualization
```{r, warning=FALSE, message=FALSE}

blood_child_zlength<- blood_child_who_stan %>% 
                     select(starts_with("zlength_"))


vis_miss(blood_child_zlength)
gg_miss_var(blood_child_zlength)

```

## boxplot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_zlength_long <- blood_child_who_stan %>% 
                          pivot_longer(
                                  cols = starts_with("zlength_"),
                                  names_to = "zlength_time",
                                  names_prefix = "zlength_",
                                  values_to = "zlength_value",
                                  values_drop_na = FALSE
                                  ) 


blood_child_zlength_long$zlength_time <- factor(blood_child_zlength_long$zlength_time,
                                                levels = c("del_merge","wk1", "wk3", "wk6", "m3", "m6", "m12", "m18"))

## assign visit variable
blood_child_zlength_long_visit <- blood_child_zlength_long %>%
  group_by(Subject_ID) %>%
  arrange(zlength_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_child_zlength_plot1 <- blood_child_zlength_long_visit %>% 
                         ggplot(aes(x=zlength_value, fill=zlength_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(zlength_time), scale="free",independent = "all") 
               

blood_child_zlength_plot1


blood_child_zlength_plot2 <- blood_child_zlength_long_visit %>% 
                         ggplot(aes(y=zlength_value, x=zlength_time,fill=zlength_time)) + 
                         geom_boxplot()
               

blood_child_zlength_plot2
```

# zbmi
## summary statistics
```{r, warning=FALSE, message=FALSE}
zbmi_table<-  blood_child_who_stan %>%
              select(zbmi_del_merge,
                     zbmi_wk1,
                     zbmi_wk3,
                     zbmi_wk6,
                     zbmi_m3,
                     zbmi_m6,
                     zbmi_m12,
                     zbmi_m18) %>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

zbmi_table
```



## missing visualization
```{r, warning=FALSE, message=FALSE}

blood_child_zbmi<- blood_child_who_stan %>% 
                     select(starts_with("zbmi_"))


vis_miss(blood_child_zbmi)
gg_miss_var(blood_child_zbmi)

```

## boxplot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_zbmi_long <- blood_child_who_stan %>% 
                          pivot_longer(
                                  cols = starts_with("zbmi_"),
                                  names_to = "zbmi_time",
                                  names_prefix = "zbmi_",
                                  values_to = "zbmi_value",
                                  values_drop_na = FALSE
                                  ) 


blood_child_zbmi_long$zbmi_time <- factor(blood_child_zbmi_long$zbmi_time,
                                                levels = c("del_merge","wk1", "wk3", "wk6", "m3", "m6", "m12", "m18"))

## assign visit variable
blood_child_zbmi_long_visit <- blood_child_zbmi_long %>%
  group_by(Subject_ID) %>%
  arrange(zbmi_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_child_zbmi_plot1 <- blood_child_zbmi_long_visit %>% 
                         ggplot(aes(x=zbmi_value, fill=zbmi_time)) + 
                         geom_histogram()+
                         facet_grid2(cols=vars(zbmi_time), scale="free",independent = "all") 
               

blood_child_zbmi_plot1


blood_child_zbmi_plot2 <- blood_child_zbmi_long_visit %>% 
                         ggplot(aes(y=zbmi_value, x=zbmi_time,fill=zbmi_time)) + 
                         geom_boxplot()
               

blood_child_zbmi_plot2
```


# zwfl WHO
## summary statistics
```{r, warning=FALSE, message=FALSE}
zwfl_table<-  blood_child_who_stan %>%
              select(zwfl_WHO_del_merge,
                     zwfl_WHO_wk1,
                     zwfl_WHO_wk3,
                     zwfl_WHO_wk6,
                     zwfl_WHO_m3,
                     zwfl_WHO_m6,
                     zwfl_WHO_m12,
                     zwfl_WHO_m18) %>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

zwfl_table
```



## missing visualization
```{r, warning=FALSE, message=FALSE}

blood_child_zwfl<- blood_child_who_stan %>% 
                     select(starts_with("zwfl_WHO"))


vis_miss(blood_child_zwfl)
gg_miss_var(blood_child_zwfl)

```

## boxplot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_zwfl_long <- blood_child_who_stan %>% 
                          pivot_longer(
                                  cols = starts_with("zwfl_WHO_"),
                                  names_to = "zwfl_WHO_time",
                                  names_prefix = "zwfl_WHO_",
                                  values_to = "zwfl_WHO_value",
                                  values_drop_na = FALSE
                                  ) 


blood_child_zwfl_long$zwfl_WHO_time <- factor(blood_child_zwfl_long$zwfl_WHO_time,
                                          levels = c("del_merge","wk1", "wk3", "wk6", "m3", "m6", "m12", "m18"))

## assign visit variable
blood_child_zwfl_long_visit <- blood_child_zwfl_long %>%
  group_by(Subject_ID) %>%
  arrange(zwfl_WHO_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```


```{r, warning=FALSE, message=FALSE}
blood_child_zwfl_plot1 <- blood_child_zwfl_long_visit %>% 
                          ggplot(aes(x=zwfl_WHO_value, fill=zwfl_WHO_time)) + 
                          geom_histogram()+
                          facet_grid2(cols=vars(zwfl_WHO_time), scale="free",independent = "all") 
               

blood_child_zwfl_plot1


blood_child_zwfl_plot2 <- blood_child_zwfl_long_visit %>% 
                          ggplot(aes(y=zwfl_WHO_value, x=zwfl_WHO_time,fill=zwfl_WHO_time)) + 
                          geom_boxplot()
               

blood_child_zwfl_plot2

```


# zwfl internal
## summary statistics
```{r, warning=FALSE, message=FALSE}
zwfl_table<-  blood_child_who_stan %>%
              select(zwfl_internal_del_merge,
                     zwfl_internal_wk3,
                     zwfl_internal_wk6,
                     zwfl_internal_m3,
                     zwfl_internal_m6,
                     zwfl_internal_m12,
                     zwfl_internal_m18) %>% 
              tbl_summary(
                type=list(everything()~"continuous"),
                missing_text = "Missing"
              ) %>% 
              bold_labels()

zwfl_table
```



## missing visualization
```{r, warning=FALSE, message=FALSE}

blood_child_zwfl<- blood_child_who_stan %>% 
                     select(starts_with("zwfl_internal"))


vis_miss(blood_child_zwfl)
gg_miss_var(blood_child_zwfl)

```


## boxplot
```{r, warning=FALSE, message=FALSE}
# data preparation
## convert to long format
blood_child_zwfl_long <- blood_child_who_stan %>% 
                          pivot_longer(
                                  cols = starts_with("zwfl_internal_"),
                                  names_to = "zwfl_internal_time",
                                  names_prefix = "zwfl_internal_",
                                  values_to = "zwfl_internal_value",
                                  values_drop_na = FALSE
                                  ) 


blood_child_zwfl_long$zwfl_internal_time <- factor(blood_child_zwfl_long$zwfl_internal_time,
                                          levels = c("del_merge", "wk3", "wk6", "m3", "m6", "m12", "m18"))

## assign visit variable
blood_child_zwfl_long_visit <- blood_child_zwfl_long %>%
  group_by(Subject_ID) %>%
  arrange(zwfl_internal_time) %>%
  dplyr::mutate(visit=1:n()) %>%
  arrange(Subject_ID)


```



```{r, warning=FALSE, message=FALSE}
blood_child_zwfl_plot1 <- blood_child_zwfl_long_visit %>% 
                          ggplot(aes(x=zwfl_internal_value, fill=zwfl_internal_time)) + 
                          geom_histogram()+
                          facet_grid2(cols=vars(zwfl_internal_time), scale="free",independent = "all") 
               

blood_child_zwfl_plot1


blood_child_zwfl_plot2 <- blood_child_zwfl_long_visit %>% 
                          ggplot(aes(y=zwfl_internal_value, x=zwfl_internal_time,fill=zwfl_internal_time)) + 
                          geom_boxplot()
               

blood_child_zwfl_plot2

```


